An analysis of interrelations between economic and environmental variables in Australian Winegrowing.

### 2023-10-10 article.tex
notes on edits
additions to indtroduction

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
\begin{highlights}
 \item ???
 \item ???
 \item ????
 \item ????
\end{highlights}
\end{frontmatter}

@@

% FIXME: Stop writing chronologically. Write by significance.
% TODO: Should the models be redone as a factor of area? instead of including area? The ensemble should effectively pick this up I do not think it needs to be done.

@@

% TODO:
% %%%%%%%%%%%%%%%
% Paper setup %
%%%%%%%%%%%%%%%

% What is your topic?
Economic sustainability of vineyards.

@@

% Notes
% Contributors to the JAE should note that, in choosing subjects for articles, the objects of the Society are ‘to promote the study and teaching of agricultural economics and relevant disciplines, and their application to issues in the agricultural, food and related industries, rural communities and the environment. The relevant disciplines include economics, statistics, marketing, business management, politics, history and sociology'. Preference will be given to articles which deal either with new developments in research and methods of analysis, or apply existing methods and techniques to new problems and situations which are likely to be of general interest to the Journal’s international readership. The Journal is not a suitable publication for articles of purely local interest.  Articles should be clearly and concisely written and should normally not exceed 7,000 words. Articles greatly in excess of this limit cannot be considered for publication.

@@

% Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.  “Nothing much is known” is not sufficient justification by itself.  You have to show why the gap in knowledge is important.  Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.

@@

>>>>

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
\begin{highlights}
 \item Highlight 1
 \item Highlight 2
 \item Highlight 3
 \item Highlight 4
\end{highlights}
\end{frontmatter}

@@

@@

%%%%%%%%%%%%%%%
% Paper setup %
%%%%%%%%%%%%%%%

 There is a need for increased understanding of different underlying conditions leading to improved performance in agricultural productivity and sustainability \citep{oecdInnovationProductivitySustainability2019}.

 Specifically within the Australian Vine and Wine industry there is a need to further understand the driving relationships between resource use and economic output .
 Environmentally sustainable
 UC Davis in California has created a new green-tech winery, a sustainable entity and blueprint
 on how to differentiate a brand. Growers need to determine better and efficient ways to make
 wine, develop benchmarks with local growers and market this approach. \citep{lukemanciniUnderstandingAustralianWine2020}

@@

% Notes
% Contributors to the JAE should note that, in choosing subjects for articles, the objects of the Society are ‘to promote the study and teaching of agricultural economics and relevant disciplines, and their application to issues in the agricultural, food and related industries, rural communities and the environment. The relevant disciplines include economics, statistics, marketing, business management, politics, history and sociology'. Preference will be given to articles which deal either with new developments in research and methods of analysis, or apply existing methods and techniques to new problems and situations which are likely to be of general interest to the Journal’s international readership. The Journal is not a suitable publication for articles of purely local interest.  Articles should be clearly and concisely written and should normally not exceed 7,000 words. Articles greatly in excess of this limit cannot be considered for publication.
% 
% A definition of agricultural economics from the encyclopedia britanica:
% 
% agricultural economics, study of the allocation, distribution, and utilization of the resources used, along with the commodities produced, by farming. Agricultural economics plays a role in the economics of development, for a continuous level of farm surplus is one of the wellsprings of technological and commercial growth.

We study the economic outcomes of Australian vineyards and their statistical relationships to the utilisation of the resources used. This is done through analysing a new comprehensive nationwide data set using XGBoosted models. We further compare the relationships between different resources to address the extensive collinearity found within the data. XGBoosted models were used because they are able to overcome multicollinearity as well as highlight the level of importance that predictor variables have; with importance being able to be statistically defined through different measures.

applies existing techniques to a new data set

agricultural economics and relevant disciplines, and their application to issues in the agricultural, food and related industries, rural communities and the environment. The relevant disciplines include economics, statistics, marketing, business management, politics, history and sociology'. Preference will be given to articles which apply existing methods and techniques to new problems and situations which are likely to be of general interest to the Journal’s international readership. The Journal is not a suitable publication for articles of purely local interest.  Articles should be clearly and concisely written and should normally not exceed 7,000 words. Articles greatly in excess of this limit cannot be considered for publication.

@@

% Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.  “Nothing much is known” is not sufficient justification by itself.  You have to show why the gap in knowledge is important. Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.
% 
% ^ is this almost boiler plate writing at this point. Considering that not much is known but we are applying it in a specific field, in this case to economics. We can use a general, nothing is known but further understanding this for economic reasons will help to improve the economic sustainability of these practices. and that these authors have postulated about these connections etc. We can start generic and funnel it into the reasoning of importance using the journals general frame work and objectives.

@@

% TODO:
%  From the code comments~ We might want to show the relationship between revenue and operational cost! then we have an idea of how these two are related.
% # These are artefacts of. As profit can be negative it is harder to predict! We know after some further mapping that both operational costs and gross margin have a cubic root relationships to the logarithm of other variables. An interesting relationship to have!
% # 
% # Importantly this cubic root relationship exists between operational costs and gross margin, which is worth noting. However we want to know what tips it either side of them being equal as that shows that a vineyard is profitable!!
